RILS-ROLS: Robust Symbolic Regression via Iterated Local Search and Ordinary Least Squares

### 2022-11-01 doc/paper.tex
Start with statistical evaluation

\end{itemize}
The above-mentioned benchmark sets may be biased as models which describe physical laws may have various symmetries, periodically w.r.t. some variables, internal separability on some variables etc. In that way, the search process and the search space can be biased and in-advance significantly reduced. Thus, some methods may get significant help with this regards, while some others may be in the subordinate situation. 
  In order to permit any kind of favoritism, we generate a set of randomly generated instances, called \textsc{Random}. These instances are generated according the following procedure. \fxnote{Opisati proceduru generisanja instanci + kombinaciju parametara za instance, itd.}

@@

\subsection{Statistical evaluation}
 \fxnote{TODO}
\section{Conclusions and future work}\label{sec:conclusions}

>>>>

\end{itemize}
The above-mentioned benchmark sets may be biased as models which describe physical laws usually have  symmetries, periodicity w.r.t. some variables, internal separability on some variables etc. In that way, the search process and the search space can be biased and in-advance significantly reduced. Thus, some methods may get significant help with this regards, while some others may be in the subordinate situation. 
  In order to permit any kind of favoritism, we generate a set of randomly generated instances, called \textsc{Random}. These instances are generated according the following procedure. \fxnote{Opisati proceduru generisanja instanci + kombinaciju parametara za instance, itd.}

All (15) competitor algorithms were run once per each instance.

@@

\subsection{Statistical evaluation}

In order to check the statistical significance of the obtained differences between the studied approaches, we employed the statistical methodology which is outlined below. This concerns the 15 approaches on two real-world benchmark sets, \textsc{Feynman} and \textsc{Strogatz}. Initially, Friedman’s test was separately executed for all competitor approaches.      In those cases in which the null hypothesis $H_0$ was rejected ($H_0$ states that there are no statistical differences between the results of the competitor approaches) pairwise comparisons are further performed by using the Nemenyi post-hoc test~\cite{pohlert2014pairwise}. The outcome is represented by means of critical difference (CD) plots. In a CD plot, the competitor approaches are placed on the horizontal axis according to their average ranking. Thereafter, the CD score is computed for a significance level of 0.05. If the difference is small enough, meaning that no statistical difference is detected, a horizontal bar linking statistically equal approaches is displayed.  \fxnote{Marko: continue}

\section{Conclusions and future work}\label{sec:conclusions}
